### 2024-10-16 texts/paper_closing.tex
add keywords, organizational contributions

% Created 2024-10-08 di 12:23
% Intended LaTeX compiler: pdflatex
\documentclass[12pt]{article}

@@

A recent study by \textcite{Velthuis_Gera_2024_fragility} has systematically investigated closing reasons of private museums, and I build on this research by using a more elaborate statistical model and additional data sources.
In particular, I analyze the risk associated with variables on the level of the founder, museum and environment, obtaining three main findings. 
Firstly, whereas previous research had identified the reliance on the founder as a key vulnerability, quantitative analyses show no significant increase in closing risk for museums whose founders have died or lost status in the art world.
A descriptive comparison of closing rates to other museum populations also shows no elevated closing risk for private museums.
Secondly, private museums with unconventional names (in particular, without the term "museum", "foundation" or "collection" in the name) face a higher closing risk, which may indicate either limited recognition by third parties as potential closing reasons and/or a temporary intention by their founders from the very beginning.
Finally, private museums face higher closing risks under certain environmental conditions, such as high competition from other private museums and, unexpectedly, the presence of large audiences.
\subsection*{Private museums definition and dependency relations}

@@

Previous research into non-profit dissolution has often investigated competition as a cause of closure, with both qualitative and quantitative studies indeed identifying competition as a frequent closure reason.
Qualitative studies which trace the history and/or closing reasons for each organization individually have highlighted competition over funding.
\textcite{Hager_1999_demise} reports that "both individual donations/subscriptions and community and corporate grants tended to go to the singular, most reputable arts organizations of their types" (p.173), resulting in "strong competitive pressures" for the vast majority of organizations (ibid.).
Similarly, \textcite{HernandezOrtiz_2022_discontinuity} found that an "[increasingly] crowded niche increased the competition and limited [NPOs'] access to resources and clients" (p.116) with an informant stating that "there was less money to go around and more organizations seeking the money [\ldots{}] we had a full-time grant writer, we were always applying for grants. But there are so many organizations applying for the same grants" (ibid.).
Quantitative studies have identified a relation between competition and non-profit closing primarily via measuring competition over density \parencite{Park_Shon_Lu_2021_mortality,Haugh_etal_2021_nascent,Lu_Shon_Zhang_2019_dissolution}, with higher number of non-profits increasing the chance of non-profit dissolution.
Thus, a hypothesis regarding competition can be formulated as:

>>>>

% Created 2024-10-16 wo 10:48
% Intended LaTeX compiler: pdflatex
\documentclass[12pt]{article}

@@

A recent study by \textcite{Velthuis_Gera_2024_fragility} has systematically investigated closing reasons of private museums, and I build on this research by using a more elaborate statistical model and additional data sources.
In particular, I analyze the risk associated with variables on the level of the founder, museum and environment, obtaining three main findings. 
Firstly, whereas previous research had identified the reliance on the founder as a key vulnerability, quantitative analyses show no significant increase in closing risk for museums whose founders have died or lost status in the art world.
A descriptive comparison of closing rates to other museum populations also shows no elevated closing risk for private museums.
Secondly, private museums with unconventional names (in particular, without the term "museum", "foundation" or "collection" in the name) face a higher closing risk, which may indicate either limited recognition by third parties as potential closing reasons and/or a temporary intention by their founders from the very beginning.
Finally, private museums face higher closing risks under certain environmental conditions, such as high competition from other private museums and, unexpectedly, the presence of large audiences.

Beyond private museums, this study highlights how organizational dissolution can be investigated via their key decision makers.
While a rich literature on non-profit survival exists, it focuses primarily organization-level variables; and previous studies that have investigated the relation between closing and key personnel variables have been limited by small samples \parencite{Searing_2020_zombies}, ad-hoc data collection \parencite{Chambre_Fatt_2002_liability} or sampling on the dependent variable \parencite{HernandezOrtiz_2022_discontinuity,Hager_etal_1996_grave}.
It furthermore advances the measurement of key constructs in organizational research, in particular legitimacy via naming conventions and competition via geospatial methods and datasets.
\subsection*{Private museums definition and dependency relations}

@@

Previous research into non-profit dissolution has often investigated competition as a cause of closure, with both qualitative and quantitative studies indeed identifying competition as a frequent closure reason.
Qualitative studies which trace the history and/or closing reasons for each organization individually have highlighted competition over funding.
\textcite{Hager_1999_demise} reports that "both individual donations/subscriptions and community and corporate grants tended to go to the singular, most reputable arts organizations of their types" (p.173), resulting in "strong competitive pressures" for the vast majority of organizations (ibid.).
Similarly, \textcite{HernandezOrtiz_2022_discontinuity} found that an "[increasingly] crowded niche increased the competition and limited [NPOs'] access to resources and clients" (p.116) with an informant stating that "there was less money to go around and more organizations seeking the money [\ldots{}] we had a full-time grant writer, we were always applying for grants. But there are so many organizations applying for the same grants" (ibid.).
Quantitative studies have identified a relation between competition and non-profit closing primarily via measuring competition via density \parencite{Park_Shon_Lu_2021_mortality,Haugh_etal_2021_nascent,Lu_Shon_Zhang_2019_dissolution}, with higher number of non-profits increasing the chance of non-profit dissolution.
Thus, a hypothesis regarding competition can be formulated as:
